Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2018-12-28 vesicle_code/docs/adhesion/adhesion.tex
starting extensional section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow}

@@

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially place symmetrically on the $y$ axis so that the background
velocity drives the vesicles towards one another.  We vary the reduced
area and the two vdW parameters and characterize the possible steady
state configurations.  For all the simulations, the length of the
vesicles are fixed, while the area is changed to achieve the desired
reduced area.

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
is $0.8$, background flow strength is $\chi = 10^{-2}$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
is $0.8$, background flow strength is $\chi = 10^{-2}$.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, and the result is
that the distance between the vesicles goes to infinity.  However, in
the presence of adhesion, is it possible that the adhesive force keeps
the vesicles from separating, resulting in the formation of a {\em
doublet}~\cite{}.

>>>>

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow}

@@

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state, the extensional background
flow is started.  We use this example to characterize the required
extensional rate to overcome the adhesive forces at for vesicles with
different reduced areas.  For all the simulations, the length of the
vesicles are fixed, while the area is changed to achieve the desired
reduced area.

%We consider two vesicles suspended in the extensional flow $\uu =
%\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
%initially place symmetrically on the $y$ axis so that the background
%velocity drives the vesicles towards one another.  We vary the reduced
%area and the two vdW parameters and characterize the possible steady
%state configurations.  For all the simulations, the length of the
%vesicles are fixed, while the area is changed to achieve the desired
%reduced area.
%
%\begin{figure}[htp]
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
%  \caption{Two vesicles in an extensional flow.  The reduced area is
%  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
%\end{figure}
%
%\begin{figure}[htp]
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
%  \caption{Two vesicles in an extensional flow.  The reduced area is
%  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
%\end{figure}

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, and the result is
that the distance between the vesicles goes to infinity.  However, in
the presence of adhesion, is it possible that the adhesive force keeps
the vesicles from separating, resulting in the formation of a {\em
doublet}~\cite{}.
